---
title: "Where are we from?"
output: flexdashboard::flex_dashboard

---
Readme first
=====================================     

**This website is meant to visualize which countries in this world HOOPP employees have a strong connection to** 

**The survey question:** 

List all and any cities and or countries you feel as if you have a connection with. You might have been born there, your spouse might have been born, you might have never been there but you eat cuisine from that 
country on a weekly basis and you plan to visit as soon as COVID is over. Anything goes, we want to 
visualize the countries we all connect with and share it with you. Over the course of the year we will enhance the map and use the data to provide relevant content!

**The Data:**

The current map is using a random sample of 200 cities from world.cities dataset. 

We can collect the data in any format however a survey with output in excel would be ideal with columns for cities and countries. After correcting for incorrect and missing values the dataset is 
joined with the world.cities dataset which provides the longitude for latitude of the cities. If we plan to build on this
we can collect more information about the countries and cities and continue to layer the map. 

**The Tech:**

This website was built using the following open source software and packages:

 - [R](https://www.r-project.org/)
 - [RMarkdown](https://rmarkdown.rstudio.com/) 
 - [Leaflet](https://rstudio.github.io/leaflet/) 
 - [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/index.html)
 - [maps](https://cran.r-project.org/web/packages/maps/maps.pdf)
 - [tidyverse](https://www.tidyverse.org/)

The output is a static html file which we should be able to host on Sharepoint with 
little to no configuration. See link below 

https://sharepoint.handsontek.net/2019/06/13/how-to-host-a-static-html-site-on-sharepoint/

**A Couple Why's**

*Why don't we just ask where are you born or what country do you come from?*

There are a number of reasons why wouldn't want to ask such a direct question just a few are below that I could think of, I think it would be a good exercise as a group to come up with reasons why such a direct 
question could 

-  An employee could have fled their home country to seek haven in Canada and they 
may still feel uncomfortable identifying where they born in fear of reprisals. 

- We may only get so many people to answer the survey, and if respondents answer
with only one country or city it will be sparsely populated map. The more data points
the better. 

*Why open source? * 

A couple of reasons, first being the output is a static html file. All the data
is within that file and requires no connections to databases etc. It should be able 
to be hosted our SharePoint seamlessly. If this project gains wide spread engagement at HOOPP it would be awesome to be able to share the same the tool with ERG's outside of HOOPP. Writing this tool 
using open source software makes this much easier to do. Vice versa if an outside ERG would like to contribute to the development of the tool they could as well. Note that none of the location data would reside in the open source repository that would all be stored in house. 

*Why not more features right away?*

We could use this tool as a working project layering the map with markers, shapes 
etc etc as the year goes on to keep people engaged with our group and getting feedback along the way. 

Capital City Markers
=====================================     
    
Column {data-width=1000}
-------------------------------------
    
### We all come from somewhere!

This map simply marks the capital cities and labels the countries that employees most connect with.  
    
```{r}
library(flexdashboard)
library(tidyverse)
library(leaflet)
library(maps)
library(htmlwidgets)

data(world.cities)

# Select 200 random countries
survey_results <- slice_sample(world.cities, n = 200)

capital_cites <- world.cities %>% 
  filter(capital == 1)

grouped_countries <- survey_results %>% 
  group_by(country.etc) %>% 
  tally() %>% 
  left_join(capital_cites, by = c("country.etc"))

grouped_countries %>% 
  leaflet() %>%
  addTiles() %>%
  addCircles(label = ~paste("", country.etc), popup = ~name)

```

Radius Based On Counts
=====================================     

    
Column {data-width=1000}
-------------------------------------
    
### We all come from somewhere!

This maps marks a circle around the capital cities that employees most connect with. 
The more people that associate with a particular city the larger the radius of the 
circle. 
    
```{r}

grouped_countries %>% 
  leaflet() %>%
  addTiles() %>%
  addCircles(label = ~paste("", country.etc), 
              radius = ~(n * 100000)  , popup = ~name)

```
